\LARGE \bf Matrix Multiplication-Driven Repulsive Fields for Manipulator Kinematic Obstacle Avoidance

### 2024-03-20 Articles/IROS/root.tex
fixed equations that broke line

\begin{equation}
	\label{eq: interp x}
	\vec{V}rep_{xyz,jk} = \vec{V}rep_{xyz,0jk}(1 - \Delta x) + \vec{V}rep_{xyz,1jk} \, \Delta x \quad \forall \, j, k \in \{1, 2\}
\end{equation}

\alert{equations break column}

\begin{equation}
	\label{eq: interp y}
	\vec{V}rep_{xyz,k} = \vec{V}rep_{xyz,0k}(1 - \Delta y) + \vec{V}rep_{xyz,1k} \, \Delta y \quad \forall \, k \in \{1, 2\}
\end{equation}

@@

\begin{figure}
	\centering
	\includegraphics[width=1\linewidth]{demo-field1c.eps} % Replace 'example-image' with the filename of your image
	\caption{Visualization of the potential field calculated for the entire map using the proposed approach. Top: Obstacle distribution via a 2D heatmap. Center: Induced repulsive fields along X (left) and Y (right) axes. Bottom: Composite vector field showcasing the resultant repulsive velocities for obstacle avoidance.}
	\label{fig:example-field}
\end{figure}

\comment{}{fix units in  plots}

@@

\add{describe weights and distributions used in experiments the kernels}

\add{sigmoid weights}

>>>>

%\begin{equation}
%	\label{eq: interp x}
%	\vec{V}rep_{xyz,jk} = \vec{V}rep_{xyz,0jk}(1 - \Delta x) + \vec{V}rep_{xyz,1jk} \, \Delta x \quad \forall \, j, k \in \{1, 2\}
%\end{equation}

\begin{equation}
\begin{aligned}
	\vec{V}rep_{xyz,jk} = &\vec{V}rep_{xyz,0jk}(1 - \Delta x) \\
	&+ \vec{V}rep_{xyz,1jk} \, \Delta x \quad \forall \, j, k \in \{1, 2\}
\end{aligned}
\end{equation}

%\begin{equation}
%	\label{eq: interp y}
%	\vec{V}rep_{xyz,k} = \vec{V}rep_{xyz,0k}(1 - \Delta y) + \vec{V}rep_{xyz,1k} \, \Delta y \quad \forall \, k \in \{1, 2\}
%\end{equation}

\begin{equation}
	\begin{aligned}
		\vec{V}rep_{xyz,k} = &\vec{V}rep_{xyz,0k}(1 - \Delta y) \\
		&+ \vec{V}rep_{xyz,1k} \, \Delta y \quad \forall \, k \in \{1, 2\}
	\end{aligned}
\end{equation}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{demo-field1c.eps} % Replace 'example-image' with the filename of your image
	\caption{Visualization of the potential field calculated for the entire map using the proposed approach. Top: Obstacle distribution via a 2D heatmap. Center: Induced repulsive fields along X (left) and Y (right) axes. Bottom: Composite vector field showcasing the resultant repulsive velocities for obstacle avoidance.}
	\label{fig:example-field}
\end{figure}

@@
